Project Protocol

### 2019-10-15 protocol.Rmd
clean lineups folder

---
title: "Project Protocol"
author: "Stephanie"
date: "27/08/2019"
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
    number_sections: yes
---

@@

#	Title
Assessing the effectiveness of different visualisation methods for Australian spatial data.
 - Including acronym (if appropriate) and version number

@@

Dorling (2011) suggests alternative map displays that aim for ‘equitable representation design’ present each member of a society equally. They are considered more ‘socially just’ but also help to present an honest display of the experiences of the whole population (Dent, 1972). This work aims to determine if using a coloured hexagon display is a more effective method of communicating the spatial relationship between a set of areas on a map.

##	Rationale/justification (i.e. how the research will fill any gaps, contribute to the field of research or contribute to existing or improved practice)

@@

 - Study type/design
 - Randomisation
 - Study methodology (eg rationale for choices of method/s; tied to project aims/objectives)
 - Research project setting (physical sites, online forums and alternatives)

@@

##	Recruitment strategies, timeframe (as required in addition to that outlined in your ethics application)
Recruitment will take place via advertising on the Figure-Eight dashboards.
The Figure-Eight platform will advertise this as a “job” to potential participants, they will not be under any obligation to complete this task. We will have the opportunity to wait until enough participants have completed the survey and provided their judgements.

@@

 XXX

#	Statistical plan
XXX

The design of this study is based on work by Hofmann, Follett, Majumder and Cook.

> The probability that an observer picks the data plot just by chance, i.e. when it is really *not* different from the other null plots, is 1=m. If an observer is able to identify the data plot from the lineup, we reject the null hypothesis. This sets our Type I error rate, a, at a level of 1=m.

@@

The authors also define how to estimate the power of a lineup: the ratio of correct identifications of the real data, x, out of n viewings.

@@

##	Data security (including how will you store)

##	Training

##	Record retention (how you will archive/destroy the information that you collect)

##	Secondary use (including providing access, disclosing)

>>>>

---
title: "Project Protocol"
output:
  pdf_document:
    toc: yes
    number_sections: yes
  word_document:
    toc: yes
bibliography: protocol.bib
link-citations: yes
---

@@

#	Title
Assessing the effectiveness of different visualisation methods for Australian spatial data.

@@

@ACTUC suggests alternative map displays that aim for ‘equitable representation design’ present each member of a society equally. They are considered more ‘socially just’ but also help to present an honest display of the experiences of the whole population [@NISCC]. This work aims to determine if using a coloured hexagon display is a more effective method of communicating the spatial relationship between a set of areas on a map.

##	Rationale/justification

@@

@@

##	Recruitment strategies, timeframe 
Recruitment will take place via advertising on the Figure-Eight dashboards.
The Figure-Eight platform will advertise this as a “job” to potential participants, they will not be under any obligation to complete this task. We will have the opportunity to wait until enough participants have completed the survey and provided their judgements.

@@

#	Statistical plan

The design of this study is based on work by Hofmann, Follett, Majumder and Cook [-@GTPCCD].

@@

This sets our Type I error rate, $\alpha$, at a level of $1/m$.
The authors also define how to estimate the power of a lineup: the ratio of correct identifications of the real data, x, out of n viewings.

@@

##	Data security
All the survey information will be stored on github, a publicly available site, as well as on site at QUT.

##	Record retention
The records of data and analysis undertaken will be stored on github as well as on site at QUT.

##	Secondary use 
The analysis scripts and the data collected will be available for secondary use. Thisn their consent form. will be disclosed to participants
